---
title: "GCV2"
author: "Felicia Zhang"
date: '2017-05-10'
output: html_document
---

```{r}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(broom)
library(tidyr)
library(wesanderson)

#Import data
raw <- readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/GazeConV2/Data/Experiment2/GazeConV2_rawdata.rds")
final <- readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/GazeConV2/Data/Experiment2/GazeConV2_preprocessed_final.rds")

#label learning trials 1-3, 13-15
final$learningtrials <- 1
final$learningtrials[final$TRIAL_INDEX > 15] <- 0
final$learningtrials[final$TRIAL_INDEX > 3 & final$TRIAL_INDEX < 13] <- 0
```

Code if sample is looking to target or not
```{r}
raw$RIGHT_GAZE_X <- as.integer(raw$RIGHT_GAZE_X)

#Subjects are looking but not at target
raw$lookattarget <- 0

#Subjects are looking at target if X coordinates are within 250-500 or 780-1030
raw$lookattarget[raw$RIGHT_GAZE_X > 249 & raw$RIGHT_GAZE_X < 501] <- 1
raw$lookattarget[raw$RIGHT_GAZE_X > 779 & raw$RIGHT_GAZE_X < 1031] <- 1

#Subjects are looking off the computer screen, computer screen is 1024 x 1280
raw$lookattarget[raw$RIGHT_GAZE_X < 0] <- 99
raw$lookattarget[raw$RIGHT_GAZE_X > 1280] <- 99

#No data collected
raw$lookattarget[is.na(raw$RIGHT_GAZE_X)] <- 999

#lookattarget 0 = screen, 1 = target, 99 = off the screen, 999 = no data

raw$RIGHT_GAZE_X <- as.integer(raw$RIGHT_GAZE_X)
######################################################################################################
#Subjects are looking but not at target
final$lookattarget <- 0

#Subjects are looking at target if X coordinates are within 250-500 or 780-1030
final$lookattarget[final$RIGHT_GAZE_X > 249 & final$RIGHT_GAZE_X < 501] <- 1
final$lookattarget[final$RIGHT_GAZE_X > 779 & final$RIGHT_GAZE_X < 1031] <- 1

#Subjects are looking off the computer screen, computer screen is 1024 x 1280
final$lookattarget[final$RIGHT_GAZE_X < 0] <- 99
final$lookattarget[final$RIGHT_GAZE_X > 1280] <- 99

#lookattarget 0 = screen, 1 = target, 99 = off the screen
```

Count how many times subject sees target in a trial using raw DF
```{r}
#Remove baseline video from data analysis
raw.novid <- subset(raw, TIMECODE < 10001)

#Keep messages that indicate when subjects looked at target
looking <- subset(raw.novid, SAMPLE_MESSAGE=="LookingAtTarget 1" | SAMPLE_MESSAGE=="LookingAtTarget 2" | SAMPLE_MESSAGE=="LookingAtTarget 3" | SAMPLE_MESSAGE=="LookingAtTarget 3"| SAMPLE_MESSAGE=="LookingAtOmission")

#Count how many times they saw targets in each trial, ignoring the trials where they saw 0 targets
looking$count <- 1
subs <- unique(looking$subID)

moo <- data.frame(subID=numeric(),trialnum=numeric(),trialtype=numeric(),condition=numeric(),targetcount=numeric())

for (j in 1:length(subs)) {
  trials <- unique(looking$TRIAL_INDEX[looking$subID==subs[j]])
  print(subs[j])
  for (i in 1:length(trials)) {
    a <- subset(looking, subID==subs[j] & TRIAL_INDEX==trials[i])
    num <- a$count
    if (length(num)==1){
      m <- c(subs[j],trials[i],a$trialtype[1],a$condition[1],1)
      moo <- rbind(moo,m)
    } else {
      for (k in 2:length(num)) {
        diffintime <- a$TIMECODE[k] - a$TIMECODE[k-1]
        #if the difference between these 2 messages is over 2000ms apart, it means they're separate
        if (diffintime > 2000) {
          a$count[k] <- k  
        }
      }
      m <- c(subs[j],trials[i],a$trialtype[1],a$condition[1],max(a$count))
      moo <- rbind(moo,m)
    }
  }}
names(moo)[1] <- "subID"
names(moo)[2] <- "trialnum"
names(moo)[3] <- "trialtype"
names(moo)[4] <- "condition"
names(moo)[5] <- "numtarg"

#Fill in Targcount (contains all trials) with the info
Targcount <- group_by(raw.novid,subID,TRIAL_INDEX,trialtype) %>%
  summarise(
    trialnum = unique(condition)
  )

Targcount$numtarg <- 0

for (j in 1:length(moo$subID)) {
  a <- moo$subID[j]
  b <- moo$trialnum[j]
  Targcount$numtarg[Targcount$subID==a & Targcount$TRIAL_INDEX==b] <- moo$numtarg[j]
}

#Fill main DF with info
for (j in 1:length(Targcount$subID)) {
  a <- Targcount$subID[j]
  b <- Targcount$TRIAL_INDEX[j]
  raw.novid$Targseen[raw.novid$subID==a & raw.novid$TRIAL_INDEX==b] <- Targcount$numtarg[j]
  }
```

Count how many times subject sees target in a trial using final DF
```{r}
#Remove baseline video from data analysis
final.novid <- subset(final, TIMECODE < 10001)

#Keep messages that indicate when subjects looked at target
looking <- subset(final.novid, SAMPLE_MESSAGE=="LookingAtTarget 1" | SAMPLE_MESSAGE=="LookingAtTarget 2" | SAMPLE_MESSAGE=="LookingAtTarget 3" | SAMPLE_MESSAGE=="LookingAtTarget 3"| SAMPLE_MESSAGE=="LookingAtOmission")

#Count how many times they saw targets in each trial, ignoring the trials where they saw 0 targets
looking$count <- 1
subs <- unique(looking$subID)

moo <- data.frame(subID=numeric(),trialnum=numeric(),trialtype=numeric(),condition=numeric(),targetcount=numeric())

for (j in 1:length(subs)) {
  trials <- unique(looking$TRIAL_INDEX[looking$subID==subs[j]])
  print(subs[j])
  for (i in 1:length(trials)) {
    a <- subset(looking, subID==subs[j] & TRIAL_INDEX==trials[i])
    num <- a$count
    if (length(num)==1){
      m <- c(subs[j],trials[i],a$trialtype[1],a$condition[1],1)
      moo <- rbind(moo,m)
    } else {
      for (k in 2:length(num)) {
        diffintime <- a$TIMECODE[k] - a$TIMECODE[k-1]
        #if the difference between these 2 messages is over 2000ms apart, it means they're separate
        if (diffintime > 2000) {
          a$count[k] <- k  
        }
      }
      m <- c(subs[j],trials[i],a$trialtype[1],a$condition[1],max(a$count))
      moo <- rbind(moo,m)
    }
  }}
names(moo)[1] <- "subID"
names(moo)[2] <- "trialnum"
names(moo)[3] <- "trialtype"
names(moo)[4] <- "condition"
names(moo)[5] <- "numtarg"

#Fill in Targcount (contains all trials) with the info
Final.Targcount <- group_by(final.novid,subID,TRIAL_INDEX,trialtype) %>%
  summarise(
    trialnum = unique(condition)
  )

Final.Targcount$numtarg <- 0

for (j in 1:length(moo$subID)) {
  a <- moo$subID[j]
  b <- moo$trialnum[j]
  Final.Targcount$numtarg[Final.Targcount$subID==a & Final.Targcount$TRIAL_INDEX==b] <- moo$numtarg[j]
}

#Fill main DF with info
for (j in 1:length(Final.Targcount$subID)) {
  a <- Final.Targcount$subID[j]
  b <- Final.Targcount$TRIAL_INDEX[j]
  final.novid$Targseen[final.novid$subID==a & final.novid$TRIAL_INDEX==b] <- Final.Targcount$numtarg[j]
}

```

Plot: how many times subjects on average saw stimuli in a trial
```{r}
#each trial is 10s long and audio and visual are both 1s each
#max number is ~5 x per trial (5 * 24 = 120)
foo <- group_by(Final.Targcount, subID) %>%
  summarise(
    meanTarget=mean(numtarg,na.rm = TRUE),
    seTarget=sd(numtarg, na.rm = TRUE)/sqrt(length(numtarg))
  )

limits <- aes(ymax = meanTarget + seTarget, ymin=meanTarget - seTarget)

ggplot(foo,aes(x=factor(subID),y=meanTarget))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  labs(x = "Subject", y = "Times viewed target")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(plot.title = element_text(hjust = 0.5))
```

Plot: Percent of trials where babies do not see target vs trials they see target at least once
```{r}
#Number of trials where babies do not look at target
foo <- subset(Targcount, numtarg==0)

Notlooking <- group_by(foo,subID) %>%
  summarise(
    totalnumoftrials = length(unique(foo$TRIAL_INDEX))
  )
Notlooking$percent <- 0

#Percent of trials where babies do not look at target: Divide number of trials where babies are not looking with total number of trials completed
for (j in 1:length(Notlooking$percent)) {
  a <- Notlooking$subID[j]
  Notlooking$percent[Notlooking$subID==a] <- length(unique(foo$TRIAL_INDEX[foo$subID==a])) / Notlooking$totalnumoftrials[j]
}
Notlooking$looking <- 0

#Calculate percent of trials where babies are looking (i.e. 1 - Notlooking$percent)
Looking <- Notlooking
Looking$percent <- 1 - Notlooking$percent
Looking$looking <- 1

#Combine DFs
Lookingfinal <- rbind(Looking,Notlooking)

#Plot
ggplot(Lookingfinal,aes(x=factor(subID),y=percent,color=factor(looking),fill=factor(looking)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  labs(x = "Subject", y = "Percent of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.2))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_manual(values = wes_palette("Moonrise3"))+
  scale_fill_manual(values = wes_palette("Moonrise3"),name="Trial type",breaks=c("0","1"),labels=c("0 looks to target", "Look to target at least once"))+
  theme(legend.position = "bottom")+
  guides(color=FALSE)+
  geom_hline(yintercept = mean(Lookingfinal$percent[Lookingfinal$looking==1]),size=1.5)

mean(Lookingfinal$percent[Lookingfinal$looking==1]) #73%

######################################################################################################
#Number of trials where babies do not look at target
foo <- subset(Final.Targcount, numtarg==0)

Notlooking <- group_by(foo,subID) %>%
  summarise(
    totalnumoftrials = length(unique(foo$TRIAL_INDEX))
  )
Notlooking$percent <- 0

#Percent of trials where babies do not look at target: Divide number of trials where babies are not looking with total number of trials completed
for (j in 1:length(Notlooking$percent)) {
  a <- Notlooking$subID[j]
  Notlooking$percent[Notlooking$subID==a] <- length(unique(foo$TRIAL_INDEX[foo$subID==a])) / Notlooking$totalnumoftrials[j]
}
Notlooking$looking <- 0

#Calculate percent of trials where babies are looking (i.e. 1 - Notlooking$percent)
Looking <- Notlooking
Looking$percent <- 1 - Notlooking$percent
Looking$looking <- 1

#Combine DFs
Lookingfinal <- rbind(Looking,Notlooking)

#Plot
ggplot(Lookingfinal,aes(x=factor(subID),y=percent,color=factor(looking),fill=factor(looking)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  labs(x = "Subject", y = "Percent of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.2))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_manual(values = wes_palette("Moonrise3"))+
  scale_fill_manual(values = wes_palette("Moonrise3"),name="Trial type",breaks=c("0","1"),labels=c("0 looks to target", "Look to target at least once"))+
  theme(legend.position = "bottom")+
  guides(color=FALSE)+
  geom_hline(yintercept = mean(Lookingfinal$percent[Lookingfinal$looking==1]),size=1.5)

mean(Lookingfinal$percent[Lookingfinal$looking==1]) #57.2%
```

On average, what percentage of a trial did we remove for each subject?
```{r}
foo <- group_by(raw.novid, subID,TRIAL_INDEX) %>%
  summarise(
    totalsample = length(unique(TIMECODE))
  )

for (j in 1:length(foo$subID)) {
  a <- foo$subID[j]
  b <- foo$TRIAL_INDEX[j]
  c <- length(unique(final.novid$TIMECODE[final.novid$subID==a & final.novid$TRIAL_INDEX==b]))
  foo$percentremoved[j] <- c / foo$totalsample[j]
}

foo2 <- group_by(foo,subID) %>%
  summarise(
    meanPERCENT=mean(percentremoved,na.rm = TRUE),
    sePERCENT=sd(percentremoved, na.rm = TRUE)/sqrt(length(percentremoved))
  )

limits <- aes(ymax = meanPERCENT + sePERCENT, ymin=meanPERCENT - sePERCENT)

ggplot(foo2,aes(x=factor(subID),y=meanPERCENT))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  ggtitle("Percent of samples removed for a trial")+
  labs(x = "Subject", y = "Percent")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.2))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "bottom")+
  guides(color=FALSE)+
  geom_errorbar(limits, width=0.25,color="black")+
  geom_hline(yintercept = mean(foo2$meanPERCENT),color="coral",size=1.5)+
  theme(plot.title = element_text(hjust = 0.5))

mean(foo2$meanPERCENT)
```

Using raw DF
For the trials where babies are looking at target, for each subject plot:
1. Percentage looking at target 
2. Percentage not looking at target
      A. Percentage not looking on screen
      B. Percentage looking on screen but not target
```{r}
#Only look at trials where babies seen Targ 
rawlooking <- subset(raw.novid, Targseen > 0)

#Calculate proportion of where they're looking for each trial
#lookattarget 0 = screen, 1 = target, 99 = off the screen, 999 = no data
rawlooking$target[rawlooking$lookattarget == 1] <- 1 
rawlooking$offscreen[rawlooking$lookattarget == 99] <- 1 
rawlooking$screen[rawlooking$lookattarget == 0] <- 1 
rawlooking$nodata[rawlooking$lookattarget == 999] <- 1

#replace NA with 0
rawlooking$target[is.na(rawlooking$target)] <- 0
rawlooking$offscreen[is.na(rawlooking$offscreen)] <- 0
rawlooking$screen[is.na(rawlooking$screen)] <- 0
rawlooking$nodata[is.na(rawlooking$nodata)] <- 0

poo <- group_by(rawlooking, subID, TRIAL_INDEX) %>%
  summarise(
    percent.targ = sum(target) / sum(target + offscreen + screen + nodata),
    percent.offscreen = sum(offscreen) / sum(target + offscreen + screen + nodata),
    percent.screen = sum(screen) / sum(target + offscreen + screen + nodata),
    percent.nodata = sum(nodata) / sum(target + offscreen + screen + nodata)
  )

#It should add up to 1
poo$total <- poo$percent.targ + poo$percent.offscreen + poo$percent.screen + poo$percent.nodata

#Get average for each subject  
poo2 <- group_by(poo, subID) %>%
  summarise(
    percent.targ2 = mean(percent.targ),
    percent.offscreen2 = mean(percent.offscreen),
    percent.screen2 = mean(percent.screen),
    percent.nodata2 = mean(percent.nodata)
  )

#Reshape wide to long
poo3 <- gather(poo2, condition, percent, percent.targ2:percent.nodata2, factor_key=TRUE)

#Plot
ggplot(poo3,aes(x=factor(subID),y=percent,color=factor(condition),fill=factor(condition)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  labs(x = "Subject", y = "Percent of a trial")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.2))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_manual(values = wes_palette("Royal1"))+
  scale_fill_manual(values = wes_palette("Royal1"),name="Trial type", breaks=c("percent.targ2", "percent.offscreen2","percent.screen2","percent.nodata2"), labels=c("Looking at target","Off screen","On screen","No data"))+
  theme(legend.position = "bottom")+
  guides(color=FALSE)
```

Using FINAL DF
For the trials where babies are looking at target, for each subject plot:
1. Percentage looking at target 
2. Percentage not looking at target
      A. Percentage not looking on screen
      B. Percentage looking on screen but not target
```{r}
#Only look at trials where babies seen Targ 
finallooking <- subset(final.novid, Targseen > 0)

#Calculate proportion of where they're looking for each trial
#lookattarget 0 = screen, 1 = target, 99 = off the screen, 999 = no data
finallooking$target[finallooking$lookattarget == 1] <- 1 
finallooking$offscreen[finallooking$lookattarget == 99] <- 1 
finallooking$screen[finallooking$lookattarget == 0] <- 1 
finallooking$nodata[finallooking$lookattarget == 999] <- 1

#replace NA with 0
finallooking$target[is.na(finallooking$target)] <- 0
finallooking$offscreen[is.na(finallooking$offscreen)] <- 0
finallooking$screen[is.na(finallooking$screen)] <- 0
finallooking$nodata[is.na(finallooking$nodata)] <- 0

poo <- group_by(finallooking, subID, TRIAL_INDEX) %>%
  summarise(
    percent.targ = sum(target) / sum(target + offscreen + screen + nodata),
    percent.offscreen = sum(offscreen) / sum(target + offscreen + screen + nodata),
    percent.screen = sum(screen) / sum(target + offscreen + screen + nodata),
    percent.nodata = sum(nodata) / sum(target + offscreen + screen + nodata)
  )

#It should add up to 1
poo$total <- poo$percent.targ + poo$percent.offscreen + poo$percent.screen + poo$percent.nodata

#Get average for each subject  
poo2 <- group_by(poo, subID) %>%
  summarise(
    percent.targ2 = mean(percent.targ),
    percent.offscreen2 = mean(percent.offscreen),
    percent.screen2 = mean(percent.screen),
    percent.nodata2 = mean(percent.nodata)
  )

#Reshape wide to long
poo3 <- gather(poo2, condition, percent, percent.targ2:percent.nodata2, factor_key=TRUE)

#Plot
ggplot(poo3,aes(x=factor(subID),y=percent,color=factor(condition),fill=factor(condition)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  labs(x = "Subject", y = "Percent of a trial")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.2))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_manual(values = wes_palette("Royal1"))+
  scale_fill_manual(values = wes_palette("Royal1"),name="Trial type", breaks=c("percent.targ2","percent.screen2"), labels=c("Looking at target","On screen"))+
  theme(legend.position = "bottom")+
  guides(color=FALSE)
```

Using raw DF
For the trials where babies are NOT looking at target, for each subject plot:
1. Percentage not looking at target
      A. Percentage not looking on screen
      B. Percentage looking on screen but not target
```{r}
#Only look at trials where babies DONT seen Targ 
raw.notlooking <- subset(raw.novid, Targseen == 0)

#Calculate proportion of where they're looking for each trial
#lookattarget 0 = screen, 1 = target, 99 = off the screen, 999 = no data
raw.notlooking$offscreen[raw.notlooking$lookattarget == 99] <- 1 
raw.notlooking$screen[raw.notlooking$lookattarget == 0] <- 1 
raw.notlooking$nodata[raw.notlooking$lookattarget == 999] <- 1

#replace NA with 0
raw.notlooking$offscreen[is.na(raw.notlooking$offscreen)] <- 0
raw.notlooking$screen[is.na(raw.notlooking$screen)] <- 0
raw.notlooking$nodata[is.na(raw.notlooking$nodata)] <- 0

roo <- group_by(raw.notlooking, subID, TRIAL_INDEX) %>%
  summarise(
    percent.offscreen = sum(offscreen) / sum(offscreen + screen + nodata),
    percent.screen = sum(screen) / sum(offscreen + screen + nodata),
    percent.nodata = sum(nodata) / sum(offscreen + screen + nodata)
  )

#It should add up to 1
roo$total <- roo$percent.offscreen + roo$percent.screen + roo$percent.nodata

#Get average for each subject  
roo2 <- group_by(roo, subID) %>%
  summarise(
    percent.targ2 = 0,
    percent.offscreen2 = mean(percent.offscreen),
    percent.screen2 = mean(percent.screen),
    percent.nodata2 = mean(percent.nodata)
  )

#Reshape wide to long
roo3 <- gather(roo2, condition, percent, percent.targ2:percent.nodata2, factor_key=TRUE)

#Plot
ggplot(roo3,aes(x=factor(subID),y=percent,color=factor(condition),fill=factor(condition)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  labs(x = "Subject", y = "Percent of a trial")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.2))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_manual(values = wes_palette("Royal1"))+
  scale_fill_manual(values = wes_palette("Royal1"),name="Trial type", breaks=c("percent.offscreen2","percent.screen2", "percent.nodata2"), labels=c("Off screen","On screen", "No data"))+
  theme(legend.position = "bottom")+
  guides(color=FALSE)
```

Using FINAL DF
After removing bad samples, on average the time babies spend looking at the screen per trial
```{r}
boo <- group_by(final.novid, subID, TRIAL_INDEX) %>%
  summarise(
    triallength = length(unique(TIMECODE))*4
  )

boo2 <- group_by(boo, subID) %>%
  summarise(
    meanLENGTH=mean(triallength,na.rm = TRUE),
    seLENGTH=sd(triallength, na.rm = TRUE)/sqrt(length(triallength))
  )

limits <- aes(ymax = meanLENGTH + seLENGTH, ymin=meanLENGTH - seLENGTH)

#Plot
ggplot(boo2,aes(x=factor(subID),y=meanLENGTH))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  ggtitle("Looking on screen")+
  labs(x = "Subject", y = "Time (ms)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_errorbar(limits, width=0.25,color="black")+
  scale_y_continuous(limits=c(0,9000),breaks=seq(0,9000,1000))+
  geom_hline(yintercept = mean(boo2$meanLENGTH),color="coral",size=1.5)
```

Using FINAL DF
After removing bad samples, on average the time babies spend looking at the target per trial
```{r}
boo <- group_by(final.novid, subID, TRIAL_INDEX,lookattarget) %>%
  summarise(
    triallength = length(unique(TIMECODE))*4
  )

#only want duration of when babies look at target
boo <- subset(boo, lookattarget==1)

boo2 <- group_by(boo, subID) %>%
  summarise(
    meanLENGTH=mean(triallength,na.rm = TRUE),
    seLENGTH=sd(triallength, na.rm = TRUE)/sqrt(length(triallength))
  )

limits <- aes(ymax = meanLENGTH + seLENGTH, ymin=meanLENGTH - seLENGTH)

#Plot
ggplot(boo2,aes(x=factor(subID),y=meanLENGTH))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  ggtitle("Looking at target")+
  labs(x = "Subject", y = "Time (ms)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_errorbar(limits, width=0.25,color="black")+
  scale_y_continuous(limits=c(0,7000),breaks=seq(0,7000,1000))+
  geom_hline(yintercept = mean(boo2$meanLENGTH),color="coral",size=1.5)
```

PDR response (2 x 2: condition x trial type)
excluding sub 19
including learning trials
```{r}
#remove video
poo <- subset(final, TIMECODE < 10001)

#keep everyone but sub 19
poo2 <- subset(poo, subID !=19)

#compare average pupil response for omission vs present
goo <- group_by(poo2, subID, condition, trialtype) %>%
  summarise(
    meanPUPIL=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )

goo2 <- group_by(goo, condition, trialtype) %>%
  summarise(
    meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),
    sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))
  )

limits <- aes(ymax = meanPUPILSs + sePUPIL, ymin=meanPUPILSs - sePUPIL)
label <- c(`1` = "AV",`2` = "VA")

ggplot(goo2,aes(x=factor(trialtype),y=meanPUPILSs,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(legend.position="none")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,.2),breaks=seq(0,.2,0.05))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

#2 x 2 ANOVA
goo$subID <- as.factor(goo$subID)
goo$condition <- as.factor(goo$condition)
goo$trialtype <- as.factor(goo$trialtype)

res.aov3 <- aov(meanPUPIL ~ condition*trialtype + Error(subID/(condition*trialtype)), data=goo)
summary(res.aov3)
```

PDR response (2 x 2: condition x trial type)
remove familiarzation trials
```{r}
#remove video
poo <- subset(final, TIMECODE < 10001)

#keep everyone but sub 19
poo2 <- subset(poo, subID !=19)

#remove familiarzation trials
poo3 <- subset(poo2, learningtrials==0)

#compare average pupil response for omission vs present
goo <- group_by(poo3, subID, condition, trialtype) %>%
  summarise(
    meanPUPIL=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )

goo2 <- group_by(goo, condition, trialtype) %>%
  summarise(
    meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),
    sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))
  )

limits <- aes(ymax = meanPUPILSs + sePUPIL, ymin=meanPUPILSs - sePUPIL)
label <- c(`1` = "AV",`2` = "VA")

ggplot(goo2,aes(x=factor(trialtype),y=meanPUPILSs,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(legend.position="none")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,.2),breaks=seq(0,.2,0.05))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

#2 x 2 ANOVA
goo$subID <- as.factor(goo$subID)
goo$condition <- as.factor(goo$condition)
goo$trialtype <- as.factor(goo$trialtype)

res.aov3 <- aov(meanPUPIL ~ condition*trialtype + Error(subID/(condition*trialtype)), data=goo)
summary(res.aov3)
```

PDR response (2 x 2: condition x trial type)
Using samples where babies ARE looking at target
```{r}
#remove video
poo <- subset(final, TIMECODE < 10001)

#keep everyone but sub 19
poo2 <- subset(poo, subID !=19)

#remove familiarzation trials
poo3 <- subset(poo2, learningtrials==0)

#keep samples where babies are LOOKING at target
poo4 <- subset(poo3, lookattarget==1)

#compare average pupil response for omission vs present
goo <- group_by(poo4, subID, condition, trialtype) %>%
  summarise(
    meanPUPIL=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )

goo2 <- group_by(goo, condition, trialtype) %>%
  summarise(
    meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),
    sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))
  )

limits <- aes(ymax = meanPUPILSs + sePUPIL, ymin=meanPUPILSs - sePUPIL)
label <- c(`1` = "AV",`2` = "VA")

ggplot(goo2,aes(x=factor(trialtype),y=meanPUPILSs,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(legend.position="none")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,.2),breaks=seq(0,.2,0.05))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

#2 x 2 ANOVA
goo$subID <- as.factor(goo$subID)
goo$condition <- as.factor(goo$condition)
goo$trialtype <- as.factor(goo$trialtype)

res.aov3 <- aov(meanPUPIL ~ condition*trialtype + Error(subID/(condition*trialtype)), data=goo)
summary(res.aov3)
```

PDR response (2 x 2: condition x trial type)
Using samples where babies ARE NOT looking at target
```{r}
#remove video
poo <- subset(final, TIMECODE < 10001)

#keep everyone but sub 19
poo2 <- subset(poo, subID !=19)

#remove familiarzation trials
poo3 <- subset(poo2, learningtrials==0)

#keep samples where babies are NOT LOOKING at target
poo4 <- subset(poo3, lookattarget==0)

#compare average pupil response for omission vs present
goo <- group_by(poo4, subID, condition, trialtype) %>%
  summarise(
    meanPUPIL=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )

goo2 <- group_by(goo, condition, trialtype) %>%
  summarise(
    meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),
    sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))
  )

limits <- aes(ymax = meanPUPILSs + sePUPIL, ymin=meanPUPILSs - sePUPIL)
label <- c(`1` = "AV",`2` = "VA")

ggplot(goo2,aes(x=factor(trialtype),y=meanPUPILSs,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(legend.position="none")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,.2),breaks=seq(0,.2,0.05))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

#2 x 2 ANOVA
goo$subID <- as.factor(goo$subID)
goo$condition <- as.factor(goo$condition)
goo$trialtype <- as.factor(goo$trialtype)

res.aov3 <- aov(meanPUPIL ~ condition*trialtype + Error(subID/(condition*trialtype)), data=goo)
summary(res.aov3)
```

How many targets do babies usually see each trial?
including trials where babies see 0
```{r}
loo <- group_by(final.novid, subID, condition, trialtype) %>%
  summarise(
    meantarg=mean(Targseen,na.rm = TRUE)
  )

loo2 <- group_by(loo, condition, trialtype) %>%
  summarise(
    meanTARG=mean(meantarg,na.rm = TRUE),
    seTARG=sd(meantarg, na.rm = TRUE)/sqrt(length(meantarg))
  )

limits <- aes(ymax = meanTARG + seTARG, ymin=meanTARG - seTARG)

label <- c(`1` = "AV",`2` = "VA")

ggplot(loo2,aes(x=factor(trialtype),y=meanTARG,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Times viewed target")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(legend.position="none")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(limits=c(0,2),breaks=seq(0,2,0.5))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

#RESULT: babies view targets the same number of times for the two different trial types and for the 2 conditions

#2 x 2 ANOVA
loo$subID <- as.factor(loo$subID)
loo$condition <- as.factor(loo$condition)
loo$trialtype <- as.factor(loo$trialtype)

res.aov3 <- aov(meantarg ~ condition*trialtype + Error(subID/(condition*trialtype)), data=loo)
summary(res.aov3)

```

```{r}

```
