---
title: "GCV2"
author: "Felicia Zhang"
date: '2017-05-10'
output: html_document
---

```{r}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(broom)
library(tidyr)
library(wesanderson)

#Import data
raw <- readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/GazeConV2/Data/Experiment2/GazeConV2_preprocessed.rds")
```
Condition
1 = AV -> VA 
2 = VA -> AV

Counterbalance
1 = AV -> VA 
2 = VA -> AV

Trialtype
1 = present
0 = omission

Fill in Counterbalance order: 1 - AV -> VA, and 2 is VA -> AV
``` {r}
raw$counterbalance <- 9

subs <- unique(raw$subID)

for (i in 1:length(subs)) {
  z <- unique(raw$condition[raw$subID==subs[i]][1:10])
  raw$counterbalance[raw$subID==subs[i]] <- z
}
```

Plot number of participants in each counterbalancing order
```{r}
foo <- group_by(raw, counterbalance) %>%
  summarise(
    numofsubs = length(unique(subID))
  )

ggplot(foo, aes(x = factor(counterbalance), y = numofsubs, fill = factor(counterbalance)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  ggtitle("All subjects")+
  labs(x = "Counterbalance", y = "Number of subjects")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(limits=c(0,26),breaks=seq(0,26,2))+
  scale_x_discrete(breaks=c("1","2"),labels=c("AV/VA", "VA/AV"))+
  theme(legend.position="none")+
  geom_text(aes(label=numofsubs), vjust=-0.5, size=6)

```

Number of trials completed for each subject
```{r}
foo <- group_by(raw, subID, condition) %>%
  summarise(
    numoftrials = length(unique(TRIAL_INDEX))
  )

foo$numoftrials[foo$condition==2] <- foo$numoftrials[foo$condition==2]*-1

ggplot(foo, aes(x = factor(subID), y = numoftrials, fill = factor(condition)))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity", width = .6)+
  ggtitle("Number of trials completed")+
  labs(x = "Subject ID", y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(breaks = seq(-14,14,2),labels=abs(seq(-14,14,2)))+ 
  coord_flip()+
  theme(legend.position="top")+
  scale_fill_discrete(name="Block",breaks=c("1","2"),labels=c("AV", "VA"))
```

Remove bad subjects (more than 50% of data missing)
```{r}
#remove bad subjects
foo <- group_by(raw, subID) %>%
  summarise(
    missingdata = length(which(is.na(RIGHT_PUPIL_SIZE))),
    totaldata = n()
  )

foo$percentmissing <- foo$missingdata / foo$totaldata

# which subjects have less than 50% good trials
z <- foo$subID[which(foo$percentmissing > 0.5)]

# remove those subjects (RECORDING_SESSION_LABEL 44 and 47 must remove)
final <- subset(raw, subID != 3)
final <- subset(final, subID != 9)
final <- subset(final, subID != 11)
final <- subset(final, subID != 12)
final <- subset(final, subID != 16)
final <- subset(final, subID != 17)
final <- subset(final, subID != 18)
final <- subset(final, subID != 19)
final <- subset(final, subID != 24)
final <- subset(final, subID != 27)
final <- subset(final, subID != 32)
final <- subset(final, subID != 36)
final <- subset(final, subID != 37)
final <- subset(final, subID != 40)
final <- subset(final, subID != 41)
unique(final$subID)
```

Remove bad trials (more than 50% of data missing)
```{r}
final <- subset(final, percentmissing < 0.5)

foo <- group_by(final, subID, condition) %>%
  summarise(
    numoftrials = length(unique(TRIAL_INDEX))
  )

foo$numoftrials[foo$condition==2] <- foo$numoftrials[foo$condition==2]*-1

ggplot(foo, aes(x = factor(subID), y = numoftrials, fill = factor(condition)))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity", width = .6)+
  ggtitle("Number of trials completed")+
  labs(x = "Subject ID", y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(breaks = seq(-14,14,2),labels=abs(seq(-14,14,2)))+ 
  coord_flip()+
  theme(legend.position="top")+
  scale_fill_discrete(name="Block",breaks=c("1","2"),labels=c("AV", "VA"))

subs <- unique(final$subID)
```

plot number of participants in each counterbalancing order
``` {r}
foo <- group_by(final, counterbalance) %>%
  summarise(
    numofsubs = length(unique(subID))
  )

ggplot(foo, aes(x = factor(counterbalance), y = numofsubs, fill = factor(counterbalance)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  ggtitle("Good subjects")+
  labs(x = "Counterbalance", y = "Number of subjects")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(limits=c(0,20),breaks=seq(0,20,2))+
  scale_x_discrete(breaks=c("1","2"),labels=c("AV/VA", "VA/AV"))+
  theme(legend.position="none")+
  geom_text(aes(label=numofsubs), vjust=-0.5, size=6)

```

Distribution of pupil size
```{r}
#Remove baseline video from data analysis
final.novid <- subset(final, TIMECODE < 10001)

# order by subID
final.novid <- final.novid[order(final.novid$subID),]

poo <- group_by(final.novid, subID, TRIAL_INDEX) %>%
  summarise(
    pupilsize = mean(PUPIL_CORRECTED, na.rm = TRUE)
  )

poo <- na.omit(poo)

ggplot(poo,aes(x=factor(subID),y=pupilsize,color=factor(subID),fill=factor(subID)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point()+
  labs(x = "Subject", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(labels=percent)+
  theme(legend.position="none")
```

Remove outlier trials - trials more than 2.5 SDs from the mean were removed
```{r}
subs <- unique(final.novid$subID)
final.novid$pupilaverage.trial <- 99

#calculate average pupil change for each trial
for (j in 1:length(subs)) {
  trials <- unique(final.novid$TRIAL_INDEX[final.novid$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    final.novid$pupilaverage.trial[final.novid$subID==subs[j] & final.novid$TRIAL_INDEX==trials[i]] <- mean(final.novid$PUPIL_CORRECTED[final.novid$subID==subs[j]& final.novid$TRIAL_INDEX==trials[i]],na.rm = TRUE)
  }
}

#remove trials that have NA
goo <- subset(final.novid, !is.na(pupilaverage.trial))

goo$outlier <- 0

for (j in 1:length(subs)) {
  trials <- unique(goo$TRIAL_INDEX[goo$subID==subs[j]])
  # calculate mean of pupil for one subject
  avg <- mean(goo$pupilaverage.trial[goo$subID==subs[j]],na.rm = TRUE)
  # calculate 2.5 SD 
  stdev <- sd(goo$pupilaverage.trial[goo$subID==subs[j]],na.rm = TRUE) # one SD
  up.stdev <- avg+(stdev*2.5) #upperbound
  low.stdev <- avg-(stdev*2.5) #lowerbound
  print(j)
for (i in 1:length(trials)) {
    if (goo$pupilaverage.trial[goo$subID==subs[j] & goo$TRIAL_INDEX==trials[i]][1] > up.stdev) {
      goo$outlier[goo$subID==subs[j] & goo$TRIAL_INDEX==trials[i]] <- 99 } 
  if (goo$pupilaverage.trial[goo$subID==subs[j] & goo$TRIAL_INDEX==trials[i]][1] < low.stdev) {
      goo$outlier[goo$subID==subs[j] & goo$TRIAL_INDEX==trials[i]] <- 99 }
}
}

unique(goo$outlier)

#remove outliers
final.novid <- subset(goo, outlier == 0)
```

Distribution of pupil size
```{r}
poo <- group_by(final.novid, subID, TRIAL_INDEX) %>%
  summarise(
    pupilsize = mean(PUPIL_CORRECTED, na.rm = TRUE)
  )

poo <- na.omit(poo)

ggplot(poo,aes(x=factor(subID),y=pupilsize,color=factor(subID),fill=factor(subID)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point()+
  labs(x = "Subject", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(labels=percent)+
  theme(legend.position="none")
```

Number of omission and present trials
```{r}
poo <- group_by(final.novid, subID, condition, trialtype) %>%
  summarise(
    numtrials = length(unique(TRIAL_INDEX))
  )

# ONLY AV 
foo <- subset(poo, condition ==1)

foo$numtrials[foo$trialtype==0] <- foo$numtrials[foo$trialtype==0]*-1

ggplot(foo, aes(x = factor(subID), y = numtrials, fill = factor(trialtype)))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity", width = .6)+
  ggtitle("AV")+
  labs(x = "Subject ID", y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(breaks = seq(-10,10,1),labels=abs(seq(-10,10,1)))+ 
  coord_flip()+
  theme(legend.position="top")+
  scale_fill_discrete(name="Trial type",breaks=c("0","1"),labels=c("omission", "present"))

# ONLY VA 
foo <- subset(poo, condition ==2)

foo$numtrials[foo$trialtype==0] <- foo$numtrials[foo$trialtype==0]*-1

ggplot(foo, aes(x = factor(subID), y = numtrials, fill = factor(trialtype)))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity", width = .6)+
  ggtitle("VA")+
  labs(x = "Subject ID", y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(breaks = seq(-10,10,1),labels=abs(seq(-10,10,1)))+ 
  coord_flip()+
  theme(legend.position="top")+
  scale_fill_discrete(name="Trial type",breaks=c("0","1"),labels=c("omission", "present"))

unique(final.novid$subID)

```

Remove subjects who don’t have at least 1 omission trial for each block
```{r}
# 6, 13, 8, 33, 39, 42
# remove those subjects
final.novid <- subset(final.novid, subID != 6)
final.novid <- subset(final.novid, subID != 8)
final.novid <- subset(final.novid, subID != 13)
final.novid <- subset(final.novid, subID != 33)
final.novid <- subset(final.novid, subID != 39)
final.novid <- subset(final.novid, subID != 42)

unique(final.novid$subID)
```

Data quality for each subject
```{r}
poo <- group_by(final.novid, subID, TRIAL_INDEX) %>%
  summarise(
    percentmissing = unique(percentmissing),
    percentlooking = 1 - percentmissing
  )

poo2 <- group_by(poo, subID) %>%
  summarise(
    meanLooking = mean(percentlooking),
    seLooking=sd(percentlooking, na.rm = TRUE)/sqrt(length(percentlooking))
  )

limits <- aes(ymax = meanLooking + seLooking, ymin=meanLooking - seLooking)

ggplot(poo2, aes(x = factor(subID), y = meanLooking))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity", width = .6)+
  labs(x = "Subject ID", y = "Percent looking at screen")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  geom_hline(yintercept = mean(poo2$meanLooking), color="red", size =1.5)+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.2))
```

Data quality
```{r}
poo <- group_by(final.novid, subID, TRIAL_INDEX, trialtype, condition) %>%
  summarise(
    percentmissing = unique(percentmissing),
    percentlooking = 1 - percentmissing
  )

poo2 <- group_by(poo, subID, trialtype, condition) %>%
  summarise(
    percentlooking2 = mean(percentlooking)
  )

poo3 <- group_by(poo2, trialtype, condition) %>%
  summarise(
    meanLooking = mean(percentlooking2),
    seLooking=sd(percentlooking2, na.rm = TRUE)/sqrt(length(percentlooking2))
  )

label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanLooking + seLooking, ymin=meanLooking - seLooking)

ggplot(poo3,aes(x=factor(trialtype),y=meanLooking,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Percent looking at screen")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.2))+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))
```

Code if sample is looking to target or not
```{r}
#Subjects are looking but not at target
final.novid$lookattarget <- 0

#Subjects are looking at target if X coordinates are within 250-500 or 780-1030
final.novid$lookattarget[final.novid$RIGHT_GAZE_X > 249 & final.novid$RIGHT_GAZE_X < 501] <- 1
final.novid$lookattarget[final.novid$RIGHT_GAZE_X > 779 & final.novid$RIGHT_GAZE_X < 1031] <- 1

#lookattarget 0 = screen, 1 = target
unique(final.novid$subID)
unique(final.novid$lookattarget)

saveRDS(final.novid, "GazeConV2_filtered.rds")
write.csv(final.novid, "GazeConV2_filtered.csv", row.names=TRUE) #save to computer
```

Percent looking at target
```{r}
poo <- group_by(final.novid, subID, TRIAL_INDEX, trialtype, condition) %>%
  summarise(
    lookattarget = length(which(lookattarget==1)),
    total = n(),
    percentlooking = lookattarget / total
  )

poo2 <- group_by(poo, subID, trialtype, condition) %>%
  summarise(
    percentlooking2 = mean(percentlooking, na.rm = TRUE)
  )

poo3 <- group_by(poo2, trialtype, condition) %>%
  summarise(
    meanLooking = mean(percentlooking2, na.rm = TRUE),
    seLooking=sd(percentlooking2, na.rm = TRUE)/sqrt(length(percentlooking2))
  )

# plot
label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanLooking + seLooking, ymin=meanLooking - seLooking)

ggplot(poo3,aes(x=factor(trialtype),y=meanLooking,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Percent looking at target")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.2))+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))
```

