---
title: "ICIS/BCBL GAZECON GRAPHS"
author: "Felicia Zhang"
date: '2017-05-10'
output: html_document
---

```{r}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(broom)
library(tidyr)
library(wesanderson)

#Import data
final <- readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/GazeConV2/Data/Experiment2/GazeConV2_preprocessed_final.rds")

#label learning trials 1-3, 13-15
final$learningtrials <- 1
final$learningtrials[final$TRIAL_INDEX > 15] <- 0
final$learningtrials[final$TRIAL_INDEX > 3 & final$TRIAL_INDEX < 13] <- 0
```

Code if sample is looking to target or not
```{r}
#Subjects are looking but not at target
final$lookattarget <- 0

#Subjects are looking at target if X coordinates are within 250-500 or 780-1030
final$lookattarget[final$RIGHT_GAZE_X > 249 & final$RIGHT_GAZE_X < 501] <- 1
final$lookattarget[final$RIGHT_GAZE_X > 779 & final$RIGHT_GAZE_X < 1031] <- 1

#Subjects are looking off the computer screen, computer screen is 1024 x 1280
final$lookattarget[final$RIGHT_GAZE_X < 0] <- 99
final$lookattarget[final$RIGHT_GAZE_X > 1280] <- 99

#lookattarget 0 = screen, 1 = target, 99 = off the screen
```

Count how many times subject sees target in a trial using final DF
```{r}
#Remove baseline video from data analysis
final.novid <- subset(final, TIMECODE < 10001)

#Keep messages that indicate when subjects looked at target
looking <- subset(final.novid, SAMPLE_MESSAGE=="LookingAtTarget 1" | SAMPLE_MESSAGE=="LookingAtTarget 2" | SAMPLE_MESSAGE=="LookingAtTarget 3" | SAMPLE_MESSAGE=="LookingAtTarget 3"| SAMPLE_MESSAGE=="LookingAtOmission")

#Count how many times they saw targets in each trial, ignoring the trials where they saw 0 targets
looking$count <- 1
subs <- unique(looking$subID)

moo <- data.frame(subID=numeric(),trialnum=numeric(),trialtype=numeric(),condition=numeric(),targetcount=numeric())

for (j in 1:length(subs)) {
  trials <- unique(looking$TRIAL_INDEX[looking$subID==subs[j]])
  print(subs[j])
  for (i in 1:length(trials)) {
    a <- subset(looking, subID==subs[j] & TRIAL_INDEX==trials[i])
    num <- a$count
    if (length(num)==1){
      m <- c(subs[j],trials[i],a$trialtype[1],a$condition[1],1)
      moo <- rbind(moo,m)
    } else {
      for (k in 2:length(num)) {
        diffintime <- a$TIMECODE[k] - a$TIMECODE[k-1]
        #if the difference between these 2 messages is over 2000ms apart, it means they're separate
        if (diffintime > 2000) {
          a$count[k] <- k  
        }
      }
      m <- c(subs[j],trials[i],a$trialtype[1],a$condition[1],max(a$count))
      moo <- rbind(moo,m)
    }
  }}
names(moo)[1] <- "subID"
names(moo)[2] <- "trialnum"
names(moo)[3] <- "trialtype"
names(moo)[4] <- "condition"
names(moo)[5] <- "numtarg"

#Fill in Targcount (contains all trials) with the info
Final.Targcount <- group_by(final.novid,subID,TRIAL_INDEX,trialtype) %>%
  summarise(
    trialnum = unique(condition)
  )

Final.Targcount$numtarg <- 0

for (j in 1:length(moo$subID)) {
  a <- moo$subID[j]
  b <- moo$trialnum[j]
  Final.Targcount$numtarg[Final.Targcount$subID==a & Final.Targcount$TRIAL_INDEX==b] <- moo$numtarg[j]
}

#Fill main DF with info
for (j in 1:length(Final.Targcount$subID)) {
  a <- Final.Targcount$subID[j]
  b <- Final.Targcount$TRIAL_INDEX[j]
  final.novid$Targseen[final.novid$subID==a & final.novid$TRIAL_INDEX==b] <- Final.Targcount$numtarg[j]
}
```

PDR response (2 x 2: condition x trial type)
excluding sub 19
excluding learning trials
```{r}
#remove video
poo <- subset(final, TIMECODE < 10001)

#keep everyone but sub 19
poo2 <- subset(poo, subID !=19)

#remove familiarzation trials
poo3 <- subset(poo2, learningtrials==0)

#compare average pupil response for omission vs present
goo <- group_by(poo3, subID, condition, trialtype) %>%
  summarise(
    meanPUPIL=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )

goo2 <- group_by(goo, condition, trialtype) %>%
  summarise(
    meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),
    sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))
  )

limits <- aes(ymax = meanPUPILSs + sePUPIL, ymin=meanPUPILSs - sePUPIL)
label <- c(`1` = "AV",`2` = "VA")

ggplot(goo2,aes(x=factor(trialtype),y=meanPUPILSs,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(legend.position="none")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,.2),breaks=seq(0,.2,0.05))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

#2 x 2 ANOVA
goo$subID <- as.factor(goo$subID)
goo$condition <- as.factor(goo$condition)
goo$trialtype <- as.factor(goo$trialtype)

res.aov3 <- aov(meanPUPIL ~ condition*trialtype + Error(subID/(condition*trialtype)), data=goo)
summary(res.aov3)

# condition is sig (p = 0.00386 **), 
# trialtype is sig (p=0.0204 *), 
# interaction is not significant (p=0.162)
```

How many targets do babies usually see each trial?
excluding sub 19
excluding learning trials
NOT INCLUDED IN POSTER
```{r}
#keep everyone but sub 19
foo <- subset(final.novid, subID !=19)

#remove familiarzation trials
foo2 <- subset(foo, learningtrials==0)

loo <- group_by(foo2, subID, condition, trialtype,TRIAL_INDEX) %>%
  summarise(
    Targseen=mean(Targseen,na.rm = TRUE)
  )

loo2 <- group_by(loo, subID, condition, trialtype) %>%
  summarise(
    meantarg=mean(Targseen,na.rm = TRUE)
  )

loo3 <- group_by(loo2, condition, trialtype) %>%
  summarise(
    meanTARG=mean(meantarg,na.rm = TRUE),
    seTARG=sd(meantarg, na.rm = TRUE)/sqrt(length(meantarg))
  )

limits <- aes(ymax = meanTARG + seTARG, ymin=meanTARG - seTARG)

label <- c(`1` = "AV",`2` = "VA")

ggplot(loo3,aes(x=factor(trialtype),y=meanTARG,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Times viewed target for a trial")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(legend.position="none")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(limits=c(0,1.5),breaks=seq(0,1.5,0.5))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

#RESULT: babies view targets the same number of times for the two different trial types and for the 2 conditions

#2 x 2 ANOVA
loo2$subID <- as.factor(loo2$subID)
loo2$condition <- as.factor(loo2$condition)
loo2$trialtype <- as.factor(loo2$trialtype)

res.aov3 <- aov(meantarg ~ condition*trialtype + Error(subID/(condition*trialtype)), data=loo2)
summary(res.aov3)

# condition is not sig (p = 0.931), 
# trialtype is significant (p=0.0461 *), 
# interaction is significant (p=0.0386 *)
```

Plot: how many times in total do they see AV target, omission, VA target, omission (individual, average)
excluding sub 19
excluding learning trials
```{r}
#keep everyone but sub 19
foo <- subset(final.novid, subID !=19)

#remove familiarzation trials
foo2 <- subset(foo, learningtrials==0)

poo <- group_by(foo2, TRIAL_INDEX, subID, trialtype, condition) %>%
  summarise(
    Targseen = unique(Targseen)
  )

poo2 <- group_by(poo, subID, trialtype, condition) %>%
  summarise(
    TotalTargseen = sum(Targseen)
  )

poo3 <- group_by(poo2, trialtype, condition) %>%
  summarise(
    meanTOTAL = mean(TotalTargseen),
    seTOTAL=sd(TotalTargseen, na.rm = TRUE)/sqrt(length(TotalTargseen))
  )

label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanTOTAL + seTOTAL, ymin=meanTOTAL - seTOTAL)

ggplot(poo3,aes(x=factor(trialtype),y=meanTOTAL,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Times viewed target for entire experiment")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(limits=c(0,7),breaks=seq(0,7,1))+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

#2 x 2 ANOVA
poo2$subID <- as.factor(poo2$subID)
poo2$condition <- as.factor(poo2$condition)
poo2$trialtype <- as.factor(poo2$trialtype)

res.aov3 <- aov(TotalTargseen ~ condition*trialtype + Error(subID/(condition*trialtype)), data=poo2)
summary(res.aov3)

# condition is not sig (p = 0.497), 
# trialtype is significant (p= 7.37e-09 ***), 
# interaction is significant (p=0.0396 *)
```


```{r}

```
