---
title: "GCV2_BabyPilot"
author: "Felicia Zhang"
date: '2017-05-10'
output: html_document
---

```{r}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(broom)
library(tidyr)

#task info: 2 conditions (AV, VA randomized)
#3 learning trials and then omission 1/3
raw.sample <- readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/GazeConV2/Data/Experiment2/GazeConV2_preprocessed_final.rds")
```

Preparing dataframe for analysis
```{r}
#label learning trials 1-3, 13-15
raw.sample$learningtrials <- 1
raw.sample$learningtrials[raw.sample$TRIAL_INDEX > 15] <- 0
raw.sample$learningtrials[raw.sample$TRIAL_INDEX > 3 & raw.sample$TRIAL_INDEX < 13] <- 0

#label which part of the trial was baseline video
raw.sample$video <- 0
raw.sample$video[raw.sample$TIMECODE > 10000] <- 1

#exclude baseline video portion from pupil analysis 
poo <- subset(raw.sample, video==0)

#remove sub 19
poo.nosub19 <- subset(poo, subID !=19) 
```

Summary graphs PDR
1. Pupil change per subject
2. Pupil change per subject (every dot is a trial)
```{r}
####### 1. pupil change per subject #######
boo <- group_by(poo, subID, TRIAL_INDEX) %>%
  summarise(
    meanPUPIL=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )

boo2 <- group_by(boo, subID) %>%
  summarise(
    meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),
    sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))
  )

limits <- aes(ymax = meanPUPILSs + sePUPIL, ymin=meanPUPILSs - sePUPIL)

ggplot(boo2,aes(x=factor(subID),y=meanPUPILSs))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  ggtitle("PDR for each subject")+
  labs(x = "Subject", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_y_continuous(labels=percent,limits=c(-0.05,.3),breaks=seq(-0.05,.3,.05))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(plot.title = element_text(hjust = 0.5))

####### 2. pupil change per trial #######
ggplot(boo,aes(x=factor(subID),y=meanPUPIL,color=factor(subID),fill=factor(subID)))+
  geom_point()+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("PDR for each trial")+
  labs(x = "Subject", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_y_continuous(labels=percent,limits=c(-0.5,1),breaks=seq(-0.5,1,.1))+
  theme(plot.title = element_text(hjust = 0.5))+
  guides(color=FALSE,fill=FALSE)

```

Summary graphs
1. Number of trials for each condition, per subject
```{r}
coo <- group_by(poo, subID, condition) %>%
  summarise(
    numtrials=length(unique(TRIAL_INDEX,na.rm = TRUE))
  )

ggplot(coo,aes(x=factor(subID),y=numtrials,color=factor(condition),fill=factor(condition)))+
  geom_bar(stat="identity")+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("")+
  labs(x = "Subject", y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_y_continuous(limits=c(0,24),breaks=seq(0,24,2))+
  scale_fill_manual(values = wes_palette("Moonrise3"), name="Condition",breaks=c("1","2"),labels=c("AV", "VA"))+
  scale_color_manual(values = wes_palette("Moonrise3"))+
  guides(color=FALSE)+
  theme(legend.position = "bottom")+
  theme(plot.title = element_text(hjust = 0.5))

coo2 <- group_by(poo, subID, condition) %>%
  summarise(
    trialnum=min(TRIAL_INDEX,na.rm = TRUE)
  )

coo2 <- subset(coo2,trialnum < 12)

length(which(coo2$condition==1)) #21 got AV

length(which(coo2$condition==2)) #9 got VA
```

#how many times they actually saw stimuli
```{r}
looking <- subset(poo, SAMPLE_MESSAGE=="LookingAtTarget 1" | SAMPLE_MESSAGE=="LookingAtTarget 2" | SAMPLE_MESSAGE=="LookingAtTarget 3" | SAMPLE_MESSAGE=="LookingAtTarget 3"|SAMPLE_MESSAGE=="LookingAtOmission")

#count how many times they saw targets in each trial
looking$count <- 1
subs <- unique(looking$subID)

moo <- data.frame(subID=numeric(),trialnum=numeric(),trialtype=numeric(),condition=numeric(),targetcount=numeric())

for (j in 1:length(subs)) {
  trials <- unique(looking$TRIAL_INDEX[looking$subID==subs[j]])
  print(subs[j])
  for (i in 1:length(trials)) {
    a <- subset(looking, subID==subs[j] & TRIAL_INDEX==trials[i])
    num <- a$count
    if (length(num)==1){
      m <- c(subs[j],trials[i],a$trialtype[1],a$condition[1],1)
      moo <- rbind(moo,m)
    } else {
      for (k in 2:length(num)) {
        diffintime <- a$TIMECODE[k] - a$TIMECODE[k-1]
        #if the difference between these 2 messages is over 2000ms apart, it means they're separate
        if (diffintime > 2000) {
          a$count[k] <- k  
        }
      }
      m <- c(subs[j],trials[i],a$trialtype[1],a$condition[1],max(a$count))
      moo <- rbind(moo,m)
    }
  }}
names(moo)[1] <- "subID"
names(moo)[2] <- "trialnum"
names(moo)[3] <- "trialtype"
names(moo)[4] <- "condition"
names(moo)[5] <- "numtarg"

#bar graph: for condition
doo <- group_by(moo, subID, condition) %>%
  summarise(
    targseen=sum(numtarg,na.rm = TRUE)
  )

ggplot(doo,aes(x=factor(subID),y=targseen,color=factor(condition),fill=factor(condition)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  labs(x = "Subject", y = "Times viewed target")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_y_continuous(limits=c(0,50),breaks=seq(0,50,5))+
  guides(color=FALSE)+
  scale_fill_manual(values = wes_palette("Moonrise3"), name="Condition",breaks=c("1","2"),labels=c("AV", "VA"))+
  scale_color_manual(values = wes_palette("Moonrise3"))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "bottom")

#each trial is 10s long and audio and visual are both 1s each
#max number is ~5 x per trial (5 * 24 = 120)
foo <- group_by(moo, subID) %>%
  summarise(
    meanTarget=mean(numtarg,na.rm = TRUE),
    seTarget=sd(numtarg, na.rm = TRUE)/sqrt(length(numtarg))
  )

limits <- aes(ymax = meanTarget + seTarget, ymin=meanTarget - seTarget)

ggplot(foo,aes(x=factor(subID),y=meanTarget))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  labs(x = "Subject", y = "Times viewed target")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(limits=c(0,3),breaks=seq(0,3,1))

############### bar graph: for trialtype ###############
doo2 <- group_by(moo, subID, trialtype) %>% 
  summarise(
    targseen=sum(numtarg,na.rm = TRUE)
  )

ggplot(doo2,aes(x=factor(subID),y=targseen,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  labs(x = "Subject", y = "Times viewed target")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_y_continuous(limits=c(0,50),breaks=seq(0,50,5))+
  scale_fill_manual(values = wes_palette("GrandBudapest"),name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  guides(color=FALSE)+
  theme(legend.position = "bottom")+
  theme(plot.title = element_text(hjust = 0.5))

```

X and Y coordinate graph for both conditions and both trial types
```{r}
zoo <- group_by(poo.nosub19, subID, TRIAL_INDEX, condition, trialtype) %>%
  summarise(
    meanY=mean(RIGHT_GAZE_Y,na.rm = TRUE),
    meanX=mean(RIGHT_GAZE_X,na.rm = TRUE)
  )

zoo$finaltrialtype[zoo$condition==1 & zoo$trialtype==1] <- 1
zoo$finaltrialtype[zoo$condition==1 & zoo$trialtype==0] <- 2
zoo$finaltrialtype[zoo$condition==2 & zoo$trialtype==1] <- 3
zoo$finaltrialtype[zoo$condition==2 & zoo$trialtype==0] <- 4

label <- c(`1` = "AV present",`2` = "AV omission",`3` = "VA present",`4` = "VA omission")

ggplot(zoo,aes(x=meanX,y=meanY,color=factor(finaltrialtype),fill=factor(finaltrialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point()+
  labs(x = "X coordinate", y = "Y coordinate")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_x_continuous(limits=c(0,1280),breaks=seq(0,1280,300),position="top")+
  scale_y_reverse(limits = c(1024, 0))+
  theme(plot.title = element_text(hjust = 0.5))+
  facet_wrap(~finaltrialtype,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  theme(legend.position="none")
```

X and Y coordinate graph comparing condition AV with VA
```{r}
#condition 1: AV
block1 <- subset(poo.nosub19,condition==1)

doo <- group_by(block1, subID, TRIAL_INDEX) %>%
  summarise(
    meanY=mean(RIGHT_GAZE_Y,na.rm = TRUE),
    meanX=mean(RIGHT_GAZE_X,na.rm = TRUE)
  )

ggplot(doo,aes(x=meanX,y=meanY,color=factor(subID),fill=factor(subID)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point()+ggtitle("AV condition")+
  labs(x = "X coordinate", y = "Y coordinate")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_x_continuous(limits=c(0,1280),breaks=seq(0,1280,300),position="top")+
  scale_y_reverse(limits = c(1024, 0))+
  theme(plot.title = element_text(hjust = 0.5))

#condition 2: VA
block2 <- subset(poo.nosub19,condition==2)
doo2 <- group_by(block2, subID, TRIAL_INDEX) %>%
  summarise(
    meanY=mean(RIGHT_GAZE_Y,na.rm = TRUE),
    meanX=mean(RIGHT_GAZE_X,na.rm = TRUE)
  )

ggplot(doo2,aes(x=meanX,y=meanY,color=factor(subID),fill=factor(subID)))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point()+ggtitle("VA condition")+
  labs(x = "X coordinate", y = "Y coordinate")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_x_continuous(limits=c(0,1280),breaks=seq(0,1280,300),position="top")+
  scale_y_reverse(limits = c(1024, 0))+
  theme(plot.title = element_text(hjust = 0.5))
```

X and Y coordinate graph comparing trialtype omission with present
```{r}
#present trial
present <- subset(poo.nosub19,trialtype==1)
doo <- group_by(present, subID, TRIAL_INDEX) %>%
  summarise(
    meanY=mean(RIGHT_GAZE_Y, na.rm = TRUE),
    meanX=mean(RIGHT_GAZE_X,na.rm = TRUE)
  )

ggplot(doo,aes(x=meanX,y=meanY,color=factor(subID),fill=factor(subID)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point()+
  ggtitle("Present trials")+
  labs(x = "X coordinate", y = "Y coordinate")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_x_continuous(limits=c(0,1280),breaks=seq(0,1280,300),position="top")+
  scale_y_reverse(limits = c(1024, 0))+
  theme(plot.title = element_text(hjust = 0.5))

#omission trial
omission <- subset(poo.nosub19,trialtype==0)
doo3 <- group_by(omission, subID, TRIAL_INDEX) %>%
  summarise(
    meanY=mean(RIGHT_GAZE_Y, na.rm = TRUE),
    meanX=mean(RIGHT_GAZE_X,na.rm = TRUE)
  )

ggplot(doo3,aes(x=meanX,y=meanY,color=factor(subID),fill=factor(subID)))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point()+ggtitle("Omission trials")+
  labs(x = "X coordinate", y = "Y coordinate")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_x_continuous(limits=c(0,1280),breaks=seq(0,1280,300),position="top")+
  scale_y_reverse(limits = c(1024, 0))+
  theme(plot.title = element_text(hjust = 0.5))
```

How many targets do babies usually see each trial?
```{r}
loo <- group_by(moo, subID, condition, trialtype) %>%
  summarise(
    meantarg=mean(numtarg,na.rm = TRUE)
  )
loo2 <- group_by(loo, condition, trialtype) %>%
  summarise(
    meanTARG=mean(meantarg,na.rm = TRUE),
    seTARG=sd(meantarg, na.rm = TRUE)/sqrt(length(meantarg))
  )

limits <- aes(ymax = meanTARG + seTARG, ymin=meanTARG - seTARG)

label <- c(`1` = "AV",`2` = "VA")

ggplot(loo2,aes(x=factor(trialtype),y=meanTARG,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Times viewed target")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(legend.position="none")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(limits=c(0,2),breaks=seq(0,2,0.5))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

#RESULT: babies view targets the same number of times for the two different trial types and for the 2 conditions

```

PDR response (2 x 2: condition x trial type)
Using entire trial duration
```{r}
#compare average pupil response for omission vs present
goo3 <- group_by(poo.nosub19, subID, condition, trialtype) %>%
  summarise(
    meanPUPIL = mean(PUPIL_CORRECTED, na.rm = TRUE)
  )

goo4 <- group_by(goo3, condition, trialtype) %>%
  summarise(
    meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),
    sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))
    )

limits <- aes(ymax = meanPUPILSs + sePUPIL, ymin=meanPUPILSs - sePUPIL)
label <- c(`1` = "AV",`2` = "VA")

ggplot(goo4,aes(x=factor(trialtype),y=meanPUPILSs,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(legend.position="none")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,.2),breaks=seq(0,.2,0.05))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

#removing learning trials
foo <- subset(poo.nosub19, learningtrials == 0) #remove trials 1-3, 13-15

#compare average pupil response for omission vs present
goo <- group_by(foo, subID, condition, trialtype) %>%
  summarise(
    meanPUPIL=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )
goo2 <- group_by(goo, condition, trialtype) %>%
  summarise(
    meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),
    sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))
  )

limits <- aes(ymax = meanPUPILSs + sePUPIL, ymin=meanPUPILSs - sePUPIL)

label <- c(`1` = "AV",`2` = "VA")

ggplot(goo2,aes(x=factor(trialtype),y=meanPUPILSs,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(legend.position="none")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,.2),breaks=seq(0,.2,0.05))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

#2 x 2 ANOVA

```

PDR response (2 x 2: condition x trial type)
Using only samples where babies are looking at target
```{r}
#computer screen is 1024 x 1280, 1/3 of 1280 = 
#only keep samples where X coordinates are < 426 or > 852
poo.target <- subset(poo.nosub19, RIGHT_GAZE_X < 1280/3 | RIGHT_GAZE_X > 1280/3*2)

goo <- group_by(poo.target, subID, condition, trialtype) %>%
  summarise(
    meanPUPIL=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )

goo2 <- group_by(goo, condition, trialtype) %>%
  summarise(
    meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),
    sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))
  )

limits <- aes(ymax = meanPUPILSs + sePUPIL, ymin=meanPUPILSs - sePUPIL)

label <- c(`1` = "AV",`2` = "VA")

ggplot(goo2,aes(x=factor(trialtype),y=meanPUPILSs,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(legend.position="none")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,.2),breaks=seq(0,.2,0.05))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

#removing learning trials
foo <- subset(poo.target, learningtrials == 0) #remove trials 1-3, 13-15

#compare average pupil response for omission vs present
goo <- group_by(foo, subID, condition, trialtype) %>%
  summarise(
    meanPUPIL=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )

goo2 <- group_by(goo, condition, trialtype) %>%
  summarise(
    meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),
    sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))
  )

limits <- aes(ymax = meanPUPILSs + sePUPIL, ymin=meanPUPILSs - sePUPIL)
label <- c(`1` = "AV",`2` = "VA")

ggplot(goo2,aes(x=factor(trialtype),y=meanPUPILSs,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(legend.position="none")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,.2),breaks=seq(0,.2,0.05))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

```

Look at changes across the trials: number of switches between the images
```{r}
looking <- subset(poo, SAMPLE_MESSAGE=="LookingAtTarget 1" | SAMPLE_MESSAGE=="LookingAtTarget 2" | SAMPLE_MESSAGE=="LookingAtTarget 3" | SAMPLE_MESSAGE=="LookingAtTarget 3"|SAMPLE_MESSAGE=="LookingAtOmission")

#count how many times they saw targets in each trial
looking$count <- 1
subs <- unique(looking$subID)

for (j in 1:length(subs)) {
  trials <- unique(looking$TRIAL_INDEX[looking$subID==subs[j]])
  print(subs[j])
  for (i in 1:length(trials)) {
    a <- subset(looking, subID==subs[j] & TRIAL_INDEX==trials[i])
    num <- a$count
    if (length(num) > 1){
      for (k in 2:length(num)) {
        diffintime <- a$TIMECODE[k] - a$TIMECODE[k-1]
        #if the difference between these 2 messages is over 2000ms apart, it means they're separate
        if (diffintime > 2000) {
          a$count[k] <- k  
          looking$count[looking$subID==subs[j] & looking$TRIAL_INDEX==trials[i]] <- a$count
        }}}}}

TargCount <- subset(looking, select = c(1, 14,16,19,23,26,27,30,34:36))
TargCount$Image[TargCount$SAMPLE_MESSAGE=="LookingAtTarget 1"] <- 1 
TargCount$Image[TargCount$SAMPLE_MESSAGE=="LookingAtTarget 2"] <- 2
TargCount$Image[TargCount$SAMPLE_MESSAGE=="LookingAtTarget 3"] <- 3 
TargCount$Image[TargCount$SAMPLE_MESSAGE=="LookingAtTarget 4"] <- 4 
TargCount$Image[TargCount$SAMPLE_MESSAGE=="LookingAtOmission"] <- 5 

koo <- group_by(TargCount, subID, TRIAL_INDEX,TIMECODE,Image,trialtype) %>%
  summarise(
    condition=mean(condition,na.rm = TRUE)
  )

koo2 <- group_by(koo, subID,TRIAL_INDEX,trialtype,condition) %>%
  summarise(
    totaltargetviews = length(unique(TIMECODE,na.rm = TRUE)),
    uniquetargetviews = length(unique(Image,na.rm = TRUE))
  )

koo2$switch <- koo2$uniquetargetviews

z <- subset(koo2, uniquetargetviews==2)
z <- subset(z, totaltargetviews > uniquetargetviews )
koo2$switch[koo2$subID==10 & koo2$TRIAL_INDEX==11] <- 3
koo2$switch[koo2$subID==21 & koo2$TRIAL_INDEX==13] <- 3
koo2$switch[koo2$subID==21 & koo2$TRIAL_INDEX==14] <- 3
koo2$switch[koo2$subID==24 & koo2$TRIAL_INDEX==4] <- 3

koo2$switch2 <- koo2$switch - 1
koo3 <- group_by(koo2, subID,trialtype,condition) %>%
  summarise(
    meanswitch=mean(switch2,na.rm = TRUE)
  )

koo4 <- group_by(koo3,trialtype,condition) %>%
  summarise(
    meanSWITCH=mean(meanswitch,na.rm = TRUE),
    seSWITCH=sd(meanswitch, na.rm = TRUE)/sqrt(length(meanswitch))
  )

limits <- aes(ymax = meanSWITCH + seSWITCH, ymin=meanSWITCH - seSWITCH)
label <- c(`1` = "AV",`2` = "VA")

ggplot(koo4,aes(x=factor(trialtype),y=meanSWITCH,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Number of switches")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(legend.position="none")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(limits=c(0,1),breaks=seq(0,1,0.5))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

#RESULT: most of the time, babies just stare at one image/one location during the trial
```

Look at changes across the trials: duration of looking at images
hypothesis: for omission trials maybe they stare at image location longer?

Using only samples where babies are looking at target
```{r}
#computer screen is 1024 x 1280, 1/3 of 1280 = 
#only keep samples where X coordinates are < 426 or > 852
poo.target <- subset(poo.nosub19, RIGHT_GAZE_X < 1280/3 | RIGHT_GAZE_X > 1280/3*2)

noo <- group_by(poo.nosub19,subID,TRIAL_INDEX,condition,trialtype) %>%
  summarise(
    totaltime=length(unique(TIMECODE,na.rm = TRUE))
  )
noo2 <- group_by(poo.target,subID,TRIAL_INDEX,condition,trialtype) %>%
  summarise(
    totaltime=length(unique(TIMECODE,na.rm = TRUE))
  )

noo$percentlooking <- 99
subs <- unique(noo$subID)

for (j in 1:length(subs)) {
  trials <- unique(noo$TRIAL_INDEX[noo$subID==subs[j]])
  print(subs[j])
  for (i in 1:length(trials)) {
  a <- noo2$totaltime[noo2$subID==subs[j] & noo2$TRIAL_INDEX==trials[i]]
  b <- noo$totaltime[noo$subID==subs[j] & noo$TRIAL_INDEX==trials[i]] 
  if (length(a) > 0) {
  noo$percentlooking[noo$subID==subs[j] & noo$TRIAL_INDEX==trials[i]] <- a / b 
  }}}

noo3 <- subset(noo, percentlooking < 99 )
noo4 <- group_by(noo3,condition,trialtype) %>%
  summarise(
    meanLOOKING=mean(percentlooking,na.rm = TRUE),
    seLOOKING=sd(percentlooking, na.rm = TRUE)/sqrt(length(percentlooking))
  )
limits <- aes(ymax = meanLOOKING + seLOOKING, ymin=meanLOOKING - seLOOKING)
label <- c(`1` = "AV",`2` = "VA")

ggplot(noo4,aes(x=factor(trialtype),y=meanLOOKING,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Percent looking at target")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(legend.position="none")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,.8),breaks=seq(0,.8,0.1))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))
```


Timecourse: look at first omission, first present after learning, first trial
```{r}


```
