---
title: "GCV2"
author: "Felicia Zhang"
date: '2017-05-10'
output: html_document
---

```{r}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(broom)
library(tidyr)
library(wesanderson)

#Import data
raw <- readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/GazeConV2/Data/Experiment2/GazeConV2_preprocessed.rds")
```
Condition
1 = AV -> VA 
2 = VA -> AV

Counterbalance
1 = AV -> VA 
2 = VA -> AV

Trialtype
1 = present
0 = omission

Fill in Counterbalance order: 1 - AV -> VA, and 2 is VA -> AV
``` {r}
raw$counterbalance <- 9

subs <- unique(raw$subID)

for (i in 1:length(subs)) {
  z <- unique(raw$condition[raw$subID==subs[i]][1:10])
  raw$counterbalance[raw$subID==subs[i]] <- z
}
```

Plot number of participants in each counterbalancing order
```{r}
foo <- group_by(raw, counterbalance) %>%
  summarise(
    numofsubs = length(unique(subID))
  )

ggplot(foo, aes(x = factor(counterbalance), y = numofsubs, fill = factor(counterbalance)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  ggtitle("All subjects")+
  labs(x = "Counterbalance", y = "Number of subjects")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(limits=c(0,24),breaks=seq(0,24,2))+
  scale_x_discrete(breaks=c("1","2"),labels=c("AV/VA", "VA/AV"))+
  theme(legend.position="none")+
  geom_text(aes(label=numofsubs), vjust=-0.5, size=6)

```

Number of trials completed for each subject
```{r}
foo <- group_by(raw, subID, condition) %>%
  summarise(
    numoftrials = length(unique(TRIAL_INDEX))
  )

foo$numoftrials[foo$condition==2] <- foo$numoftrials[foo$condition==2]*-1

ggplot(foo, aes(x = factor(subID), y = numoftrials, fill = factor(condition)))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity", width = .6)+
  ggtitle("Number of trials completed")+
  labs(x = "Subject ID", y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(breaks = seq(-14,14,2),labels=abs(seq(-14,14,2)))+ 
  coord_flip()+
  theme(legend.position="top")+
  scale_fill_discrete(name="Block",breaks=c("1","2"),labels=c("AV", "VA"))
```

Remove bad subjects (more than 50% of data missing)
```{r}
#remove bad subjects
foo <- group_by(raw, subID) %>%
  summarise(
    missingdata = length(which(is.na(RIGHT_PUPIL_SIZE))),
    totaldata = n()
  )

foo$percentmissing <- foo$missingdata / foo$totaldata

# which subjects have less than 50% good trials
z <- foo$subID[which(foo$percentmissing > 0.5)]

# remove those subjects
final <- subset(raw, subID != 3)
final <- subset(final, subID != 9)
final <- subset(final, subID != 11)
final <- subset(final, subID != 12)
final <- subset(final, subID != 16)
final <- subset(final, subID != 17)
final <- subset(final, subID != 18)
final <- subset(final, subID != 19)
final <- subset(final, subID != 24)
final <- subset(final, subID != 27)

unique(final$subID)
```

Remove bad trials (more than 50% of data missing)
```{r}
final <- subset(final, percentmissing < 0.5)

foo <- group_by(final, subID, condition) %>%
  summarise(
    numoftrials = length(unique(TRIAL_INDEX))
  )

foo$numoftrials[foo$condition==2] <- foo$numoftrials[foo$condition==2]*-1

ggplot(foo, aes(x = factor(subID), y = numoftrials, fill = factor(condition)))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity", width = .6)+
  ggtitle("Number of trials completed")+
  labs(x = "Subject ID", y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(breaks = seq(-14,14,2),labels=abs(seq(-14,14,2)))+ 
  coord_flip()+
  theme(legend.position="top")+
  scale_fill_discrete(name="Block",breaks=c("1","2"),labels=c("AV", "VA"))

subs <- unique(final$subID)
```

plot number of participants in each counterbalancing order
``` {r}
foo <- group_by(final, counterbalance) %>%
  summarise(
    numofsubs = length(unique(subID))
  )

ggplot(foo, aes(x = factor(counterbalance), y = numofsubs, fill = factor(counterbalance)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  ggtitle("Good subjects")+
  labs(x = "Counterbalance", y = "Number of subjects")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(limits=c(0,12),breaks=seq(0,12,2))+
  scale_x_discrete(breaks=c("1","2"),labels=c("AV/VA", "VA/AV"))+
  theme(legend.position="none")+
  geom_text(aes(label=numofsubs), vjust=-0.5, size=6)

```

Distribution of pupil size
```{r}
#Remove baseline video from data analysis
final.novid <- subset(final, TIMECODE < 10001)

# order by subID
final.novid <- final.novid[order(final.novid$subID),]

poo <- group_by(final.novid, subID, TRIAL_INDEX) %>%
  summarise(
    pupilsize = mean(PUPIL_CORRECTED, na.rm = TRUE)
  )

poo <- na.omit(poo)

ggplot(poo,aes(x=factor(subID),y=pupilsize,color=factor(subID),fill=factor(subID)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point()+
  labs(x = "Subject", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(labels=percent)+
  theme(legend.position="none")
```

Remove outlier trials - trials more than 2.5 SDs from the mean were removed
```{r}
subs <- unique(final.novid$subID)
final.novid$pupilaverage.trial <- 99

#calculate average pupil change for each trial
for (j in 1:length(subs)) {
  trials <- unique(final.novid$TRIAL_INDEX[final.novid$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    final.novid$pupilaverage.trial[final.novid$subID==subs[j] & final.novid$TRIAL_INDEX==trials[i]] <- mean(final.novid$PUPIL_CORRECTED[final.novid$subID==subs[j]& final.novid$TRIAL_INDEX==trials[i]],na.rm = TRUE)
  }
}

#remove trials that have NA
goo <- subset(final.novid, !is.na(pupilaverage.trial))

goo$outlier <- 0

for (j in 1:length(subs)) {
  trials <- unique(goo$TRIAL_INDEX[goo$subID==subs[j]])
  # calculate mean of pupil for one subject
  avg <- mean(goo$pupilaverage.trial[goo$subID==subs[j]],na.rm = TRUE)
  # calculate 2.5 SD 
  stdev <- sd(goo$pupilaverage.trial[goo$subID==subs[j]],na.rm = TRUE) # one SD
  up.stdev <- avg+(stdev*2.5) #upperbound
  low.stdev <- avg-(stdev*2.5) #lowerbound
  print(j)
for (i in 1:length(trials)) {
    if (goo$pupilaverage.trial[goo$subID==subs[j] & goo$TRIAL_INDEX==trials[i]][1] > up.stdev) {
      goo$outlier[goo$subID==subs[j] & goo$TRIAL_INDEX==trials[i]] <- 99 } 
  if (goo$pupilaverage.trial[goo$subID==subs[j] & goo$TRIAL_INDEX==trials[i]][1] < low.stdev) {
      goo$outlier[goo$subID==subs[j] & goo$TRIAL_INDEX==trials[i]] <- 99 }
}
}

unique(goo$outlier)

#remove outliers
final.novid <- subset(goo, outlier == 0)
```

Distribution of pupil size
```{r}
poo <- group_by(final.novid, subID, TRIAL_INDEX) %>%
  summarise(
    pupilsize = mean(PUPIL_CORRECTED, na.rm = TRUE)
  )

poo <- na.omit(poo)

ggplot(poo,aes(x=factor(subID),y=pupilsize,color=factor(subID),fill=factor(subID)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point()+
  labs(x = "Subject", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(labels=percent)+
  theme(legend.position="none")
```

Code if sample is looking to target or not
```{r}
#Subjects are looking but not at target
final.novid$lookattarget <- 0

#Subjects are looking at target if X coordinates are within 250-500 or 780-1030
final.novid$lookattarget[final.novid$RIGHT_GAZE_X > 249 & final.novid$RIGHT_GAZE_X < 501] <- 1
final.novid$lookattarget[final.novid$RIGHT_GAZE_X > 779 & final.novid$RIGHT_GAZE_X < 1031] <- 1

#Subjects are looking off the computer screen, computer screen is 1024 x 1280
final.novid$lookattarget[final.novid$RIGHT_GAZE_X < 0] <- 99
final.novid$lookattarget[final.novid$RIGHT_GAZE_X > 1280] <- 99

#lookattarget 0 = screen, 1 = target, 99 = off the screen
```

Count how many times subject sees target in a trial using final DF 
```{r}
#Keep messages that indicate when subjects looked at target
looking <- subset(final.novid, SAMPLE_MESSAGE=="LookingAtTarget 1" | SAMPLE_MESSAGE=="LookingAtTarget 2" | SAMPLE_MESSAGE=="LookingAtTarget 3" | SAMPLE_MESSAGE=="LookingAtTarget 3"| SAMPLE_MESSAGE=="LookingAtOmission")

#Count how many times they saw targets in each trial, ignoring the trials where they saw 0 targets
looking$count <- 1
subs <- unique(looking$subID)

moo <- data.frame(subID=numeric(),trialnum=numeric(),trialtype=numeric(),condition=numeric(),targetcount=numeric())

for (j in 1:length(subs)) {
  trials <- unique(looking$TRIAL_INDEX[looking$subID==subs[j]])
  print(subs[j])
  for (i in 1:length(trials)) {
    a <- subset(looking, subID==subs[j] & TRIAL_INDEX==trials[i])
    num <- a$count
    if (length(num)==1){
      m <- c(subs[j],trials[i],a$trialtype[1],a$condition[1],1)
      moo <- rbind(moo,m)
    } else {
      for (k in 2:length(num)) {
        diffintime <- a$TIMECODE[k] - a$TIMECODE[k-1]
        #if the difference between these 2 messages is over 2000ms apart, it means they're separate
        if (diffintime > 2000) {
          a$count[k] <- k  
        }
      }
      m <- c(subs[j],trials[i],a$trialtype[1],a$condition[1],max(a$count))
      moo <- rbind(moo,m)
    }
  }}
names(moo)[1] <- "subID"
names(moo)[2] <- "trialnum"
names(moo)[3] <- "trialtype"
names(moo)[4] <- "condition"
names(moo)[5] <- "numtarg"

#Fill in Targcount (contains all trials) with the info
Final.Targcount <- group_by(final.novid,subID,TRIAL_INDEX,trialtype) %>%
  summarise(
    condition = unique(condition)
  )

Final.Targcount$numtarg <- 0

for (j in 1:length(moo$subID)) {
  a <- moo$subID[j]
  b <- moo$trialnum[j]
  Final.Targcount$numtarg[Final.Targcount$subID==a & Final.Targcount$TRIAL_INDEX==b] <- moo$numtarg[j]
}

Final.Targcount$trialtype <- NULL
Final.Targcount$condition <- NULL

#Fill main DF with info
final.novid <- merge(final.novid,Final.Targcount)

```

Plot: how many times they see AV target, omission, VA target, omission for entire experiment
```{r}
poo <- group_by(final.novid, subID, TRIAL_INDEX, trialtype, condition) %>%
  summarise(
    Targseen = unique(numtarg)
  )

poo2 <- group_by(poo, subID, trialtype, condition) %>%
  summarise(
    TotalTargseen = sum(Targseen)
  )

poo3 <- group_by(poo2, trialtype, condition) %>%
  summarise(
    meanTOTAL = mean(TotalTargseen),
    seTOTAL=sd(TotalTargseen, na.rm = TRUE)/sqrt(length(TotalTargseen))
  )

label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanTOTAL + seTOTAL, ymin=meanTOTAL - seTOTAL)

ggplot(poo3,aes(x=factor(trialtype),y=meanTOTAL,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Times seen target in experiment")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(limits=c(0,16),breaks=seq(0,16,2))+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

#for AV - every subject
pooAV <- subset(poo2, condition==1)

ggplot(pooAV,aes(x=factor(subID),y=TotalTargseen,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity",position = position_dodge(width = 0.9))+
  labs(x = "Subject", y = "Total number of times seen")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(limits=c(0,30),breaks=seq(0,30,2))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"),name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  guides(color=FALSE)

#VA condition - every subject
pooAV <- subset(poo2, condition==2)

ggplot(pooAV,aes(x=factor(subID),y=TotalTargseen,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity",position = position_dodge(width = 0.9))+
  labs(x = "Subject", y = "Total number of times seen")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(limits=c(0,30),breaks=seq(0,30,2))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"),name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  guides(color=FALSE)
```

Plot: how many times they see AV target, omission, VA target, omission for 1 trial
```{r}
# times seen target for each trial
poo <- group_by(final.novid, subID, TRIAL_INDEX, trialtype, condition) %>%
  summarise(
    Targseen = unique(numtarg)
  )

poo2 <- group_by(poo, subID, trialtype, condition) %>%
  summarise(
    TotalTargseen = mean(Targseen, na.rm = TRUE)
  )

poo3 <- group_by(poo2, trialtype, condition) %>%
  summarise(
    meanTOTAL = mean(TotalTargseen, na.rm = TRUE),
    seTOTAL=sd(TotalTargseen, na.rm = TRUE)/sqrt(length(TotalTargseen))
  )

label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanTOTAL + seTOTAL, ymin=meanTOTAL - seTOTAL)

ggplot(poo3,aes(x=factor(trialtype),y=meanTOTAL,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Times seen target in one trial")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(limits=c(0,3),breaks=seq(0,3,1))+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

```
### ORDER EFFECTS 

Plot: does counterbalancing order effect how many times they see AV present, omission, VA present, omission 
```{r}
poo <- group_by(final.novid, subID, TRIAL_INDEX, trialtype, condition, order) %>%
  summarise(
    Targseen = unique(Targseen)
  )

poo2 <- group_by(poo, subID, trialtype, condition,order) %>%
  summarise(
    TotalTargseen = sum(Targseen)
  )

poo3 <- group_by(poo2, trialtype, condition,order) %>%
  summarise(
    meanTOTAL = mean(TotalTargseen, na.rm = TRUE),
    seTOTAL=sd(TotalTargseen, na.rm = TRUE)/sqrt(length(TotalTargseen))
  )

# order 1 = AV, VA
pooAV <- subset(poo3, order ==1)
label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanTOTAL + seTOTAL, ymin=meanTOTAL - seTOTAL)

ggplot(pooAV,aes(x=factor(trialtype),y=meanTOTAL,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Total Number of times seen")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(limits=c(0,16),breaks=seq(0,16,2))+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

# order 2 = VA, AV
pooVA <- subset(poo3, order ==2)
label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanTOTAL + seTOTAL, ymin=meanTOTAL - seTOTAL)

ggplot(pooVA,aes(x=factor(trialtype),y=meanTOTAL,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Trial type", y = "Total Number of times seen")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(limits=c(0,20),breaks=seq(0,20,2))+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))

```

Plot: Order effects - pupil change from baseline, excluding samples where babies are NOT looking at the target
```{r}
# excluding samples where babies are NOT looking at the target
goo <- subset(final.novid, lookattarget==1)

#remove learning trials
goo <- subset(goo, learningtrials==0)

# calculate PDR for each subject
goo2 <- group_by(goo, subID, trialtype, condition, order) %>%
  summarise(
    meanPUPIL=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )

# collapse across subjects
goo3 <- group_by(goo2, condition, trialtype, order) %>%
  summarise(
    meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),
    sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))
  )

# order 1 = AV, VA
gooAV <- subset(goo3, order==1)
label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanPUPILSs + sePUPIL, ymin=meanPUPILSs - sePUPIL)

ggplot(gooAV,aes(x=factor(trialtype),y=meanPUPILSs,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  ggtitle("AV-VA")+
  labs(x = "Trial type", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(labels=percent,limits=c(0,.2),breaks=seq(0,.2,0.05))+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))+
  theme(plot.title = element_text(hjust = 0.5))

# order 2 = VA, AV
gooAV <- subset(goo3, order==2)
label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanPUPILSs + sePUPIL, ymin=meanPUPILSs - sePUPIL)

ggplot(gooAV,aes(x=factor(trialtype),y=meanPUPILSs,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  ggtitle("VA-AV")+
  labs(x = "Trial type", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(labels=percent,limits=c(0,.30),breaks=seq(0,.30,0.05))+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))+
  theme(plot.title = element_text(hjust = 0.5))

```

Plot: Order effects - pupil change from baseline, including samples where babies are NOT looking at the target
```{r}
#remove learning trials
goo <- subset(final.novid, learningtrials==0)

# calculate PDR for each subject
goo2 <- group_by(goo, subID, trialtype, condition, order) %>%
  summarise(
    meanPUPIL=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )

# collapse across subjects
goo3 <- group_by(goo2, condition, trialtype, order) %>%
  summarise(
    meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),
    sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))
  )

# order 1 = AV, VA
gooAV <- subset(goo3, order==1)
label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanPUPILSs + sePUPIL, ymin=meanPUPILSs - sePUPIL)

ggplot(gooAV,aes(x=factor(trialtype),y=meanPUPILSs,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  ggtitle("AV-VA")+
  labs(x = "Trial type", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(labels=percent,limits=c(0,.2),breaks=seq(0,.2,0.05))+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))+
  theme(plot.title = element_text(hjust = 0.5))

# order 2 = VA, AV
gooAV <- subset(goo3, order==2)
label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanPUPILSs + sePUPIL, ymin=meanPUPILSs - sePUPIL)

ggplot(gooAV,aes(x=factor(trialtype),y=meanPUPILSs,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  ggtitle("VA-AV")+
  labs(x = "Trial type", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(labels=percent,limits=c(0,.2),breaks=seq(0,.2,0.05))+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))+
  theme(plot.title = element_text(hjust = 0.5))
```

Plot: Order effects - times viewed target in one trial excluding trials where they are not looking
```{r}
#exclude trials where they are not looking
poo <- subset(final.novid, Targseen > 0)

loo <- group_by(poo, subID, condition, trialtype, order) %>%
  summarise(
    meantarg=mean(Targseen,na.rm = TRUE)
  )

loo2 <- group_by(loo, condition, trialtype, order) %>%
  summarise(
    meanTARG=mean(meantarg,na.rm = TRUE),
    seTARG=sd(meantarg, na.rm = TRUE)/sqrt(length(meantarg))
  )

# order 1 = AV, VA
gooAV <- subset(loo2, order==1)
label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanTARG + seTARG, ymin=meanTARG - seTARG)

ggplot(gooAV,aes(x=factor(trialtype),y=meanTARG,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  ggtitle("AV-VA")+
  labs(x = "Trial type", y = "Times viewed target")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(limits=c(0,4),breaks=seq(0,4,1))

# order 2 = VA, AV
gooAV <- subset(loo2, order==2)
label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanTARG + seTARG, ymin=meanTARG - seTARG)

ggplot(gooAV,aes(x=factor(trialtype),y=meanTARG,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  ggtitle("VA-AV")+
  labs(x = "Trial type", y = "Times viewed target")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(limits=c(0,4),breaks=seq(0,4,1))

```

Plot: Order effects - times viewed target in one trial including trials where they are not looking
```{r}
loo <- group_by(final.novid, subID, condition, trialtype, order) %>%
  summarise(
    meantarg=mean(Targseen,na.rm = TRUE)
  )

loo2 <- group_by(loo, condition, trialtype, order) %>%
  summarise(
    meanTARG=mean(meantarg,na.rm = TRUE),
    seTARG=sd(meantarg, na.rm = TRUE)/sqrt(length(meantarg))
  )

# order 1 = AV, VA
gooAV <- subset(loo2, order==1)
label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanTARG + seTARG, ymin=meanTARG - seTARG)

ggplot(gooAV,aes(x=factor(trialtype),y=meanTARG,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  ggtitle("AV-VA")+
  labs(x = "Trial type", y = "Times viewed target")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(limits=c(0,4),breaks=seq(0,4,1))

# order 2 = VA, AV
gooAV <- subset(loo2, order==2)
label <- c(`1` = "AV",`2` = "VA")
limits <- aes(ymax = meanTARG + seTARG, ymin=meanTARG - seTARG)

ggplot(gooAV,aes(x=factor(trialtype),y=meanTARG,color=factor(trialtype),fill=factor(trialtype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  ggtitle("VA-AV")+
  labs(x = "Trial type", y = "Times viewed target")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  geom_errorbar(limits, width=0.25,color="black")+
  facet_wrap(~condition,ncol=2,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(name="Trial type",breaks=c("0","1"),labels=c("Omission", "Present"))+
  scale_color_manual(values = wes_palette("GrandBudapest"))+
  scale_fill_manual(values = wes_palette("GrandBudapest"))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(limits=c(0,4),breaks=seq(0,4,1))

```

